TBD

### 2016-10-11 paper.tex
paper.tex

In general, when $\bA$ has dimensions $m\times n$, with $m > n$ we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bA\bx\|. 
\end{equation}
If $\bA^H\bA$ is invertiable then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bA^H\bA$ is singular there are an infinite amount of solutions
that minimizes Eq.~\eqref{eq:norm_ls}. Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}
The CG method is gaurenteed to converge if we use it to solve Eq.~\eqref{eq:normal_equation}.

>>>>

In general, when $\bA$ has dimensions $m\times n$, with $m > n$ we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bA\bx\|. 
\end{equation}
If $\bA^H\bA$ is invertiable then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bA^H\bA$ is singular there are an infinite amount of solutions
that minimizes Eq.~\eqref{eq:norm_ls}. Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}

The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

It should now be clear to
the reader why the CG method is espicially applicable to sparse linear systems, since in those cases $m < N^2$. 
We can improve the computational complexity of the CG method by preconditioning. 
[Preconditioning is a technique for improving the condition number of a matrix. Suppose that ' is a
symmetric, positive-definite matrix that approximates, but is easier to invert. We can solve indirectly by solving] - RW directly coppied from source
\begin{equation}
\bM^{-1}\bA\bx = \bM^{-1}\bb
\end{equation}

The best precondtioner would be the preconditioner which makes $\kappa$ unity, i.e. completly
eliminating it from the computational complexity equation. The only choice of $\bM$ which is capable of best way to do this is to chooose as preconditioner the matrix $(\bA)^{-1}$, which is what we would like to determine in the frist place.
If the diagonal entries of $\bA$ are more significant than its off-diagonal entries, then the Jacobian preconditioner is a good preconditioner to use.
